
\documentclass[11pt]{article}

\usepackage{fullpage}
\usepackage{amsmath,amssymb,amsthm,amsfonts,latexsym,bbm,xspace,graphicx,float,mathtools,
verbatim, xcolor,bm} 
\PassOptionsToPackage{hyphens}{url}\usepackage{hyperref}
\newcommand{\new}[1]{\textcolor{red}{#1}}
%\usepackage{psfig}
\usepackage{pgfplots}

\newcommand{\future}[1]{\textcolor{red}{#1}}

\newcommand{\hP}{\hat P}
\newcommand{\hp}{\hat p}

\newcommand{\Dk}{\Delta_k}
\newcommand{\Px}{P(x)}
\newcommand{\Qx}{Q(x)}
\newcommand{\Nx}{N_x}

\newcommand{\Py}{P(y)}
\newcommand{\Qy}{Q(y)}
\newcommand{\Pml}{P_{ML}}
\newcommand{\Pmlx}{\Pml(x)}
\newcommand{\Pbeta}{P_{\beta}}
\newcommand{\Pbetax}{\Pbeta(x)}

\newcommand{\dTV}[2]{d_{TV} (#1,#2)}
\newcommand{\dKL}[2]{D(#1||#2)}
\newcommand{\chisq}[2]{\chi^2(#1,#2)}
\newcommand{\eps}{\varepsilon}

\newcommand{\nPepsp}[1]{n^*(#1, \eps)}
\newcommand{\nPeps}{\nPepsp{\cP}}


\newcommand{\sumX}{\sum_{x\in\cX}}

\newcommand{\Bpr}[1]{Bern(#1)}

\newenvironment{problem}[2][Problem]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}\hskip \labelsep {\bfseries #2.}]}{\end{trivlist}}

\input{../glodef} 

\title{Assignment Five\\ ECE 4200}
\date{}

\begin{document}
\maketitle 


\begin{itemize}

\item
{\bf The due date is 10/18/2020, 23.59.59 ET}. 
\item
This assignment is primarily for us to gather information about the class. 
\end{itemize}


\noindent\textbf{Note.} Please answer to the best of your knowledge, and as truthfully as possible. Feedback will be helpful for us. We can get the data from canvas and from zoom, but this is much quicker. \textbf{You will get full points for answering the questions regardless of the answers.}

\begin{problem}{1. (25 points)}
\begin{enumerate}
\item 
 Until 10/8, how many lectures have you not seen? If you attended the lecture synchronously, or watched the video later, it is counted as being watched. Your answershould be a number between 0 and 11. 
\item
 Until 10/8, how many discussions have you not seen? If you attended the discussion synchronously, or watched the video later, it is counted as being watched. Your answer should be a number between 0 and 5. 
\item 
Is there anything we can do to increase your attendance in the lectures live?
\item
If you are not watching lectures, do you feel the notes are sufficient to solve the assignments?
\item
Do you feel the assignments are too easy or too hard?
\end{enumerate}

\end{problem}



\end{document}