
\documentclass[11pt]{article}

\usepackage{fullpage}
\usepackage{amsmath,amssymb,amsthm,amsfonts,latexsym,bbm,xspace,graphicx,float,mathtools,
verbatim, xcolor} 
\PassOptionsToPackage{hyphens}{url}\usepackage{hyperref}
\newcommand{\new}[1]{\textcolor{red}{#1}}
%\usepackage{psfig}

\newcommand{\future}[1]{\textcolor{red}{#1}}

\newcommand{\hP}{\hat P}
\newcommand{\hp}{\hat p}

\newcommand{\Dk}{\Delta_k}
\newcommand{\Px}{P(x)}
\newcommand{\Qx}{Q(x)}
\newcommand{\Nx}{N_x}

\newcommand{\Py}{P(y)}
\newcommand{\Qy}{Q(y)}
\newcommand{\Pml}{P_{ML}}
\newcommand{\Pmlx}{\Pml(x)}
\newcommand{\Pbeta}{P_{\beta}}
\newcommand{\Pbetax}{\Pbeta(x)}


\newcommand{\dTV}[2]{d_{TV} (#1,#2)}
\newcommand{\dKL}[2]{D(#1||#2)}
\newcommand{\chisq}[2]{\chi^2(#1,#2)}
\newcommand{\eps}{\varepsilon}

\newcommand{\nPepsp}[1]{n^*(#1, \eps)}
\newcommand{\nPeps}{\nPepsp{\cP}}


\newcommand{\sumX}{\sum_{x\in\cX}}

\newcommand{\Bpr}[1]{Bern(#1)}

\newenvironment{problem}[2][Problem]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}\hskip \labelsep {\bfseries #2.}]}{\end{trivlist}}

\input{../glodef} 

\title{Assignment Four\\ ECE 4200}

\begin{document}
\maketitle 

\begin{itemize}
\item
Provide credit to \textbf{any sources} other than the course staff that helped you solve the problems. This includes \textbf{all students} you talked to regarding the problems. 	
\item
You can look up definitions/basics online (e.g., wikipedia, stack-exchange, etc).
\item
{\bf The due date is 10/11/2020, 23.59.59 ET}. 
\item
Submission rules are the same as previous assignments.
\end{itemize}



\begin{problem}{1 (10 points) Different class conditional probabilities}
Consider a classification problem with features in $\RR^d$ and labels in $\{-1, +1\}$. Consider the class of linear classifiers of the form $(\bar w, 0)$, namely all the classifiers (hyper planes) that pass through the origin (or $t=0$). Instead of logistic regression, suppose the class probabilities are given by the following function, where $\bar X\in\RR^d$ are the features:
\begin{align}
P\Paren{y=+1|\bar X, \bar w} = \frac12\Paren{1+\frac{\bar w\cdot \bar X}{\sqrt{1+(\bar w\cdot \bar X)^2}}}, 
\end{align}
where $\bar w\cdot \bar X$ is the dot product between $\bar w$ and  $\bar X$. 

Suppose we obtain $n$ examples $(\bar X_i, y_i)$ for $i=1,\ldots, n$. 
\begin{enumerate}
\item 
Show that the log-likelihood function is
\begin{align}
J(\bar w) = -n\log 2 + \sum_{i=1}^{n} \log \Paren{1+ \frac{y_i (\bar w\cdot \bar X_i)}{\sqrt{1+(\bar w\cdot \bar X_i)^2}}}.
\end{align}
\item
Compute the gradient of $J(\bar w)$ and write one step of gradient ascent. Namely fill in the blank:
\begin{align}
\bar w_{j+1} = \bar w_j + \eta\cdot \underline{\hspace{3cm}}\nonumber
\end{align}
\textbf{hint:} use the chain rule and $\nabla_{\bar w} \bar w\cdot \bar X = \bar X$. 
\end{enumerate}
\end{problem}


\noindent In \textbf{Problem 2}, and \textbf{Problem 3}, we will study linear regression. We will assume in both the problems that $w^0=0$. (This can be done by translating the features and labels to have mean zero, but we will not worry about it).  For $\bar w = (w^1, \ldots, w^d)$, and $\bar X = (\bar X^1, \ldots, \bar X^d)$, the regression we want is:
\begin{align}
y = w^1 \bar X^1+\ldots + w^d \bar X^d = \bar w\cdot \bar X.
\end{align}
We considered the following regularized least squares objective, which is called as \textbf{Ridge Regression}. For the dataset $S=\{(\bar X_1, y_1), \ldots, (\bar X_n, y_n)\}$,  
\[
J(\bar w, \lambda) = \sum_{i=1}^n \Paren{y_i -\bar w\cdot \bar X_i}^2 +\lambda \cdot \|\bar w\|_2^2.
\]	
 
\begin{problem}{2 (10 points) Gradient Descent for regression}\quad

\begin{enumerate}
\item 
Instead of using the closed form expression we mentioned in class, suppose we want to perform gradient descent to find the optimal solution for $J(\bar w)$. Please compute the gradient of $J$, and write one step of the gradient descent with step size $\eta$. 
\item
Suppose we get a new point $\bar X_{n+1}$, what will the predicted $y_{n+1}$ be when $\lambda\to\infty$? 
\end{enumerate}
\end{problem}


\begin{problem}{3 (15 points) Regularization increases training error}
In the class we said that when we regularize, we expect to get weight vectors with smaller, but never proved it. We also displayed a plot showing that the training error increases as we regularize more (larger $\lambda$). In this assignment, we will formalize the intuitions rigorously.

Let $0<\lambda_1<\lambda_2$ be two regularizer values. Let $\bar w_1$, and $\bar w_2$ be the minimizers of $J(\bar w, \lambda_1)$, and $J(\bar w, \lambda_2)$ respectively. 

\begin{enumerate}
	\item Show that $\|\bar w_1\|_2^2\ge \|\bar w_2\|_2^2$. Therefore more regularization implies smaller norm of solution!
	
	\textbf{Hint:} Observe that $J(\bar w_1, \lambda_1)\le J(\bar w_2, \lambda_1)$, and $J(\bar w_2, \lambda_2)\le J(\bar w_1, \lambda_2)$ (why?). 
	\item Show that the training error for $\bar w_1$ is less than that of $\bar w_2$. In other words, show that 
\[
\sum_{i=1}^n \Paren{y_i -\bar w_1\cdot \bar X_i}^2 \le \sum_{i=1}^n \Paren{y_i -\bar w_2\cdot \bar X_i}^2.
\]

\textbf{Hint:} Use the first part of the problem.
\end{enumerate}

\end{problem}

%\begin{problem}{3 (15 points)}
%Suppose we have a classification problem, where each example $\bar X$ has $k$ \textbf{positive} features. Suppose we restrict weight vectors to be \textbf{positive}, and consider the following discriminative function:
%\[
%Pr (y= -1 | \bar X, \bar w, t ) = \frac{2}{1+\exp(\bar w\cdot \bar X-t)}.
%\]
%The positivity means that each entry of $\bar w$ is positive, and $t$ is also positive.
%\begin{enumerate}
%\item
%Find the gradient of $(\bar X\cdot \bar w)^2$ with respect to $\bar w, t$.
%\item 
%Write the log-likelihood function $\ell(\bar w, t)$ for this problem.
%\item
%Is $\ell(\bar w, t)$ concave in the positive quadrant? 
%\item
%Compute the gradient of $\ell(\bar w)$.
%\item
%Write one step of the gradient ascent step to find the maximum likelihood estimate of $\bar w$.
%\end{enumerate}
%\end{problem}




\begin{problem}{4 (25 points) Linear and Quadratic Regression}
Please refer to the Jupyter Notebook in the assignment, and complete the coding part in it!
You can use sklearn regression package: \url{http://scikit-learn.org/stable/modules/generated/sklearn.linear_model.Ridge.html}
\end{problem}





\end{document}

If the model were trained with wine training2.txt, which λ would you choose to train your final model? Why?

%
%\begin{table*}[h]
%\begin{center}
%\begin{tabular}{c|ccccc}
%{\bf Liked?} &
%{\bf Easy?} &
%{\bf AI?} &
%{\bf Sys?} &
%{\bf Thy?} &
%{\bf Morning?} \\
%\hline
%+ & y  & y  & n  & y  & n  \\
%+ & y  & y  & n  & y  & n  \\
%+ & n  & y  & n  & n  & n  \\
%+ & n  & n  & n  & y  & n  \\
%+ & n  & y  & y  & n  & y  \\
%+ & y  & y  & n  & n  & n  \\
%+ & y  & y  & n  & y  & n  \\
%+ & n  & y  & n  & y  & n  \\
%+ & n  & n  & n  & n  & y  \\
% + & y  & n  & n  & y  & y  \\
% + & n  & y  & n  & y  & n  \\
% + & y  & y  & y  & y  & y  \\
%- & y  & y  & y  & n  & y  \\
%- & n  & n  & y  & y  & n  \\
%- & n  & n  & y  & n  & y  \\
%- & y  & n  & y  & n  & y  \\
%- & n  & n  & y  & y  & n  \\
%- & n  & y  & y  & n  & y  \\
%- & y  & n  & y  & n  & n  \\
%- & y  & n  & y  & n  & y  \\
%\end{tabular}
%\end{center}
%\caption{Course rating data set}
%\label{tab:data:course}
%\end{table*}
